Appendix: Tutorials, examples, resources

### 2017-07-08 README.Rmd
Last proofread; restore missing citation to good-enough

---
title: "Excuse me, do you have a moment to talk about version control?"
authors:
- name: Jennifer Bryan
  affiliation: |
    RStudio and the Department of Statistics, University of British Columbia
  thanks: >
    The author gratefully acknowledges the constructive feedback from reviewers
    Nicholas Horton, Colin Rundel, and Hadley Wickham.
blinded: 0
output:
  github_document:
    toc: yes
  rticles::asa_article: null
keywords: |
    data science, workflow, Git, GitHub, R language, R Markdown, reproducibility
abstract: >
    Data analysis, statistical research, and teaching statistics have at least
    one thing in common&#58; these activities all produce many files! There may
    be data files, source code, figures, tables, prepared reports, and much
    more. These files generally evolve over the course of a project and often
    need to be shared with others, for reading or edits, as a project unfolds.
    Without explicit and structured management, project organization can easily
    descend into chaos, taking time away from the primary work and reducing the
    quality of the final product. This unhappy result can be avoided by
    repurposing tools and workflows from the software development world, namely,
    distributed version control. This article describes the use of the version
    control system Git and and the hosting site GitHub for statistical and data
    scientific workflows. Special attention is given to projects that use the
    statistical language R and, optionally, R Markdown documents. Supplementary
    materials include an annotated set of links to step-by-step tutorials,
    real world examples, and other useful learning resources.
bibliography: git-github-for-stats.bib
---

@@

The Git way is to track the evolution of `iris.R`, through a series of commits,
each equipped with an explanatory message. Figure \ref{fig:diy-vs-git}C depicts this linear, *in situ* development process, with development and time flowing from bottom to top. Figure \ref{fig:diy-vs-git}D shows the same history for a common collaborative Git workflow, where contributors work independently but sync regularly to a common version. Especially important versions get a human-readable tag, e.g., "draft-01", to signal a meaningful milestone. Yes, there is some pain in adopting the formalism of Git, but it is worth it.

@@

The best way to deal with merge conflicts is to prevent them. This is another reason for all parties to commit, pull, and push often. Small changes, integrated frequently, in non-binary files, are the easiest for Git to automatically merge for you. The difficulty of merging (by Git or by you) is proportional to the evolutionary distance between two lines of work. The presence of frequently-changing binary files also increases the burden. So make lots of small commits, sync regularly with GitHub, and only track binary files with good reason.

@@

__Appendix: Tutorials, examples, resources__ Provide an annotated set of links for each section of the article, including step-by-step tutorials, real world examples, and other useful learning resources.

>>>>

---
title: "Excuse me, do you have a moment to talk about version control?"
authors:
- name: Jennifer Bryan
  affiliation: |
    RStudio and the Department of Statistics, University of British Columbia
  thanks: >
    The author gratefully acknowledges the constructive feedback from reviewers
    Nicholas Horton, Colin Rundel, and Hadley Wickham.
blinded: 0
output:
  github_document:
    toc: yes
  rticles::asa_article: null
keywords: |
    data science, workflow, Git, GitHub, R language, R Markdown, reproducibility
abstract: >
    Data analysis, statistical research, and teaching statistics have at least
    one thing in common&#58; these activities all produce many files! There are
    data files, source code, figures, tables, prepared reports, and much
    more. Most of these files evolve over the course of a project and often
    need to be shared with others, for reading or edits, as a project unfolds.
    Without explicit and structured management, project organization can easily
    descend into chaos, taking time away from the primary work and reducing the
    quality of the final product. This unhappy result can be avoided by
    repurposing tools and workflows from the software development world, namely,
    distributed version control. This article describes the use of the version
    control system Git and and the hosting site GitHub for statistical and data
    scientific workflows. Special attention is given to projects that use the
    statistical language R and, optionally, R Markdown documents. Supplementary
    materials include an annotated set of links to step-by-step tutorials,
    real world examples, and other useful learning resources.
bibliography: git-github-for-stats.bib
---

@@

The Git way is to track the evolution of `iris.R`, through a series of commits,
each equipped with an explanatory message. Figure \ref{fig:diy-vs-git}C depicts this linear, *in situ* process, with development and time flowing from bottom to top. Figure \ref{fig:diy-vs-git}D shows the same history for a common collaborative Git workflow, where contributors work independently but sync regularly to a common version. Especially important versions get a human-readable tag, e.g., "draft-01", to signal a meaningful milestone. Yes, there is some pain in adopting the formalism of Git, but it is worth it.

@@

The best way to deal with merge conflicts is to prevent them. This is another reason for all parties to commit, pull, and push often. Small changes, integrated frequently, in non-binary files, are the easiest for Git to automatically merge for you. The difficulty of merging (by Git or by you) is proportional to the evolutionary distance between two lines of work [@good-enough]. The presence of frequently-changing binary files also increases the burden. So make lots of small commits, sync regularly with GitHub, and only track binary files with good reason.

@@

__Appendix: Tutorials, examples, resources__ Provides an annotated set of links for each section of the article, including step-by-step tutorials, real world examples, and other useful learning resources.

### 2017-07-08 README.tex
Last proofread; restore missing citation to good-enough

\bigskip
\begin{abstract}
Data analysis, statistical research, and teaching statistics have at
least one thing in common: these activities all produce many files!
There may be data files, source code, figures, tables, prepared reports,
and much more. These files generally evolve over the course of a project
and often need to be shared with others, for reading or edits, as a
project unfolds. Without explicit and structured management, project
organization can easily descend into chaos, taking time away from the
primary work and reducing the quality of the final product. This unhappy
result can be avoided by repurposing tools and workflows from the
software development world, namely, distributed version control. This
article describes the use of the version control system Git and and the
hosting site GitHub for statistical and data scientific workflows.
Special attention is given to projects that use the statistical language
R and, optionally, R Markdown documents.
\end{abstract}

@@

The Git way is to track the evolution of \texttt{iris.R}, through a
series of commits, each equipped with an explanatory message. Figure
\ref{fig:diy-vs-git}C depicts this linear, \emph{in situ} development
process, with development and time flowing from bottom to top. Figure
\ref{fig:diy-vs-git}D shows the same history for a common collaborative
Git workflow, where contributors work independently but sync regularly
to a common version. Especially important versions get a human-readable
tag, e.g., ``draft-01'', to signal a meaningful milestone. Yes, there is
some pain in adopting the formalism of Git, but it is worth it.

@@

The best way to deal with merge conflicts is to prevent them. This is
another reason for all parties to commit, pull, and push often. Small
changes, integrated frequently, in non-binary files, are the easiest for
Git to automatically merge for you. The difficulty of merging (by Git or
by you) is proportional to the evolutionary distance between two lines
of work. The presence of frequently-changing binary files also increases
the burden. So make lots of small commits, sync regularly with GitHub,
and only track binary files with good reason.

@@

>>>>

\bigskip
\begin{abstract}
Data analysis, statistical research, and teaching statistics have at
least one thing in common: these activities all produce many files!
There are data files, source code, figures, tables, prepared reports,
and much more. Most of these files evolve over the course of a project
and often need to be shared with others, for reading or edits, as a
project unfolds. Without explicit and structured management, project
organization can easily descend into chaos, taking time away from the
primary work and reducing the quality of the final product. This unhappy
result can be avoided by repurposing tools and workflows from the
software development world, namely, distributed version control. This
article describes the use of the version control system Git and and the
hosting site GitHub for statistical and data scientific workflows.
Special attention is given to projects that use the statistical language
R and, optionally, R Markdown documents. Supplementary materials include
an annotated set of links to step-by-step tutorials, real world
examples, and other useful learning resources.
\end{abstract}

@@

The Git way is to track the evolution of \texttt{iris.R}, through a
series of commits, each equipped with an explanatory message. Figure
\ref{fig:diy-vs-git}C depicts this linear, \emph{in situ} process, with
development and time flowing from bottom to top. Figure
\ref{fig:diy-vs-git}D shows the same history for a common collaborative
Git workflow, where contributors work independently but sync regularly
to a common version. Especially important versions get a human-readable
tag, e.g., ``draft-01'', to signal a meaningful milestone. Yes, there is
some pain in adopting the formalism of Git, but it is worth it.

@@

The best way to deal with merge conflicts is to prevent them. This is
another reason for all parties to commit, pull, and push often. Small
changes, integrated frequently, in non-binary files, are the easiest for
Git to automatically merge for you. The difficulty of merging (by Git or
by you) is proportional to the evolutionary distance between two lines
of work \citep{good-enough}. The presence of frequently-changing binary
files also increases the burden. So make lots of small commits, sync
regularly with GitHub, and only track binary files with good reason.

@@

\section{Supplementary Materials}\label{supplementary-materials}

\textbf{Appendix: Tutorials, examples, resources} Provides an annotated
set of links for each section of the article, including step-by-step
tutorials, real world examples, and other useful learning resources.

### 2017-07-08 appendix.Rmd
Refer to supplement in main article
Last proofread; restore missing citation to good-enough

---
title: "Appendix: Tutorials and examples"
output:
  github_document:
    toc: yes
  pdf_document: null
urlcolor: blue    
---

@@

I cite it in the article, but really want to underscore the accesibility of Alice Bartlett's talk "Git for Humans". Highly recommended. [Slides on Speakerdeck](https://speakerdeck.com/alicebartlett/git-for-humans).

>>>>

---
title: "Appendix: Tutorials, examples, resources"
output:
  github_document:
    toc: yes
  pdf_document: null
urlcolor: blue    
---

@@

I cite it in the article, but really want to underscore the accessibility of Alice Bartlett's talk "Git for Humans". Highly recommended. [Slides on Speakerdeck](https://speakerdeck.com/alicebartlett/git-for-humans).
